---
title: "Twilight Series Analysis"
author: "Karissa Dautenhahn"
date: "2022-12-12"
output:
  pdf_document: 
    keep_tex: yes
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  tidy.opts=list(width.cutoff=70), 
  tidy=TRUE
)
```

```{r warning = FALSE, message = FALSE}
library(kableExtra)
library(readtext)
library(cmu.textstat)
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(syuzhet)
library(ggplot2)
```

```{r}
# Twilight Series files
files_list <- list.files("~/Documents/Twilight", all.files = T, full.names = T, pattern = "*.txt") 

# Midnight Sun book
files_list_ms <- list.files("~/Documents/MidnightSun", all.files = T, full.names = T, pattern = "*.txt")

# All Edward text
files_list_ed <- list.files("~/Documents/Edward", all.files = T, full.names = T, pattern = "*.txt") 

# All Bella text
files_list_bella <- list.files("~/Documents/Bella", all.files = T, full.names = T, pattern = "*.txt") 


# Creating corpus object for Twilight Saga
sp <- files_list %>%
  readtext::readtext()
sp <-   sp %>%
  mutate(text = preprocess_text(text)) %>%
  corpus() 

# Creating a corpus object for Midnight Sun
sp_ms <- files_list_ms %>%
  readtext::readtext()
sp_ms <-   sp_ms %>%
  mutate(text = preprocess_text(text)) %>%
  corpus() 

# Corpus object for Edward 
sp_ed <- files_list_ed %>%
  readtext::readtext()
sp_ed <-   sp_ed %>%
  mutate(text = preprocess_text(text)) %>%
  corpus() 

# Corpus object for Bella 
sp_bella <- files_list_bella %>%
  readtext::readtext()
sp_bella <-   sp_bella %>%
  mutate(text = preprocess_text(text)) %>%
  corpus() 
```

# Summary of Data

Below are token counts for each of the four corpora.

```{r}
kbl(list(summary(sp)[c(1,3)], summary(sp_bella)[c(1,3)]), caption = "Summary of Twilight Series and Bella Corpora") %>% kable_classic() %>% add_header_above(c("Twilight Series Corpus" = 1, "Bella Corpus" = 1), align = "l")
kbl(list(summary(sp_ms)[c(1,3)], summary(sp_ed)[c(1,3)]), caption = "Summary of Midnight Sun and Edward Corpora") %>% kable_classic() %>% add_header_above(c("Midnight Sun Corpus" = 1, "Edward Corpus" = 1), align = "l")
```

This section contains the code to tokenize the corpus objects and create a document feature matrix for each.

```{r}
# Tokenizing all 4 corpora
sp <- sp %>%  tokens(what="fastestword", remove_numbers=TRUE)
sp_ms <- sp_ms %>%  tokens(what="fastestword", remove_numbers=TRUE)
# Using word separation to eliminate punctuation issues on Edward's corpus
sp_ed <- sp_ed %>%  tokens(what="word", remove_numbers=TRUE, remove_punct = TRUE, remove_symbols = TRUE)
sp_bella <- sp_bella %>%  tokens(what="fastestword", remove_numbers=TRUE, remove_punct = TRUE)

# Document Feature Matrices for all corpora
dfm_twilight <- dfm(sp)
dfm_ms <- dfm(sp_ms)
dfm_ed <- dfm(sp_ed)
dfm_bella <- dfm(sp_bella)
```

This chart showcases the top 10 most frequent words in the Twilight Series as well as Midnight Sun. One interesting note is that "her" is the 4th most frequent word in Midnight Sun while "he" is the 6th most frequent word in the Twilight Series.

```{r}
freq_df <- textstat_frequency(dfm_twilight) %>%
  data.frame(stringsAsFactors = F)
knitr::kable(head(freq_df[1:3], 10), caption = "Most frequent words in the Twilight Saga")

freq_df_ms <- textstat_frequency(dfm_ms) %>%
  data.frame(stringsAsFactors = F)
knitr::kable(head(freq_df_ms[1:3], 10), caption = "Most frequent words in Midnight Sun")
```


# Keyness comparison

This code chunk creates a keyness table from the Edward and Bella dfm objects. The columns for Deviation of Proportions (DP) for both the target and reference corpora are ignored since they are not used in the study. The PV column shows highly significant p-values for all of the top 5 tokens. The 5 results are shown here although the top 2 are our main interest. The remaining 3 tokens have high LL values likely due to tokenizing differences between the two corpora and should not be regarded as significantly.

```{r}
# Target DFM is Edward, reference is Bella
char_kw <- keyness_table(dfm_ed, dfm_bella)

kableExtra::kbl(head(char_kw[-c(9, 10)], n = 5), caption = "Tokens with the highest keyness values in Edward's text when compared to Bella's text", booktabs = T, linesep = "", digits = 2) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position") %>%
  kableExtra::kable_classic()
```

# Collocates by Mutual Information (MI)

The 6 collocates of "him" (from Bella's corpus) and "her" (from Edward's corpus) are shown here using an Absolute Frequency (AF) of 16 and MI score of 3. A default of 5 words to the left and 5 to the right of the node word is used.

```{r}
b <- collocates_by_MI(sp_ed, "her", left = 3, right = 0)
b <- b %>% filter(col_freq >= 16 & MI_1 >= 3)

g  <- collocates_by_MI(sp_bella, "him", left = 3, right = 0)
g <- g %>% filter(col_freq >= 16 & MI_1 >= 3)

knitr::kable(head(b), digits = 3, caption = "Top Collocates of 'her' from Edward's corpus")
knitr::kable(head(g), digits = 3, caption = "Top Collocates of 'him' from Bella's corpus")
```

# Graph of Collocates of "Him" and "Her"

A graph of collocates is created using the same parameters as before (AF >= 16, MI >= 3).

```{r,  message = FALSE, fig.width = 7, fig.height=4}
library(ggraph)
net <- col_network(b, g)

ggraph(net, weight = link_weight, layout = "stress") + 
  geom_edge_link(color = "gray80", alpha = .75) + 
  geom_node_point(aes(alpha = node_weight, size = 3, color = n_intersects)) +
  geom_node_text(aes(label = label), repel = T, size = 3) +
  scale_alpha(range = c(0.2, 0.9)) +
  theme_graph() +
  theme(legend.position="none")
```


# Sentiment Analysis

This section involves using the syuzhet package (from library(syuzhet)) to analyze the sentiment of each novel.

```{r warning = FALSE, message = FALSE}
midnight_sun_tokens <- "~/Documents/MidnightSun/MidnightSun.txt" %>% 
  readtext()
mb_mid_sun <- str_squish(midnight_sun_tokens$text[1])
# chunk the novel into sentences
mb_sentences <- get_sentences(mb_mid_sun)
nrc_data_mid_sun <- get_nrc_sentiment(mb_sentences)


twilight_tokens <- "~/Documents/Twilight/Meyer_Twilight.txt" %>%
  readtext() 
mb_twilight <- str_squish(twilight_tokens$text[1])
# chunk the novel into sentences
mb_sentences_t <- get_sentences(mb_twilight)
nrc_data_twilight <- get_nrc_sentiment(mb_sentences_t)


new_moon_tokens <- "~/Documents/Twilight/Meyer_NewMoon.txt" %>%
  readtext() 
mb_new_moon <- str_squish(new_moon_tokens$text[1])
# chunk the novel into sentences
mb_sentences_nm <- get_sentences(mb_new_moon)
nrc_data_new_moon <- get_nrc_sentiment(mb_sentences_nm)


eclipse_tokens <- "~/Documents/Twilight/Meyer_Eclipse.txt" %>%
  readtext() 
mb_eclipse <- str_squish(eclipse_tokens$text[1])
# chunk the novel into sentences
mb_sentences_ec <- get_sentences(mb_eclipse)
nrc_data_eclipse <- get_nrc_sentiment(mb_sentences_ec)


breaking_dawn_tokens <- "~/Documents/Twilight/Meyer_BreakingDawn.txt" %>%
  readtext() 
mb_breaking_dawn <- str_squish(breaking_dawn_tokens$text[1])
# chunk the novel into sentences
mb_sentences_bd <- get_sentences(mb_breaking_dawn)
nrc_data_breaking_dawn <- get_nrc_sentiment(mb_sentences_bd)


# Gathering proportions of emotions in books
midnight_sun_emotions <- colSums(prop.table(nrc_data_mid_sun[, 1:8]))
twilight_emotions <- colSums(prop.table(nrc_data_twilight[, 1:8]))
new_moon_emotions <- colSums(prop.table(nrc_data_new_moon[, 1:8]))
eclipse_emotions <- colSums(prop.table(nrc_data_eclipse[, 1:8]))
breaking_dawn_emotions <- colSums(prop.table(nrc_data_breaking_dawn[, 1:8]))

twilight_feeling_table <- rbind(twilight_emotions, new_moon_emotions, eclipse_emotions, breaking_dawn_emotions, midnight_sun_emotions)

# Vector of book names
books <- c("Twilight", "New Moon", "Eclipse", "Breaking Dawn", "Midnight Sun")

twilight_feeling_table <- cbind(books, data.frame(twilight_feeling_table, row.names=NULL))

# Creating the plot
emotion_plot <- twilight_feeling_table %>%
  pivot_longer(-c(books)) %>%
ggplot(aes(x = books, y = value, color = name)) +
geom_point(pch = 20) +
geom_smooth(method = "gam", se = F) +
geom_line(aes(group = name)) +
  scale_x_discrete(limits = books) + 
ylab("Proportion of Sentences with Given Emotion") +
xlab("Books") +
  labs(color = "Emotions") +
ggtitle("Emotions Represented throughout the Twilight Series and Midnight Sun") +
theme(plot.title = element_text(size = 12), axis.text.x = element_text(angle = 45, hjust = 1))
emotion_plot
```


Graph comparing just the first Twilight novel and Midnight Sun:

```{r warning = FALSE, message = FALSE}
emotion_plot <- twilight_feeling_table %>%
  filter(books %in% c("Twilight", "Midnight Sun")) %>%
  pivot_longer(-c(books)) %>%
ggplot(aes(x = books, y = value, color = name)) +
geom_point(pch = 20) +
geom_smooth(method = "gam", se = F) +
geom_line(aes(group = name)) +
  scale_x_discrete(limits = c("Twilight", "Midnight Sun")) + 
ylab("Proportion of Sentences with Given Emotion") +
xlab("Books") +
  labs(color = "Emotions") +
ggtitle("Emotions in Twilight and Midnight Sun") +
theme(plot.title = element_text(size = 12), axis.text.x = element_text(angle = 45, hjust = 1))
emotion_plot
```
